Collocated Deduplication with Fault Isolation for Virtual Machine Snapshot Backup

### 2013-08-29 snapshot_system/fast14_evaluation.tex
figure revisions

@@

                ymin=099.9991,
                ymax=100.0002,

@@

@@

                \addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

                \addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

                \addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                %\addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

        %\caption{100000 machine cluster.}
  \label{fig:vm-availability-100000}

>>>>

            %the expressions in this plot are simply to trick pgfplots into not expanding the y range, and don't actually change the data
            % expression used: (99.999+((y-99.999)*1000)/1000)

@@

                %ymin=099.9991,
                %ymax=100.0002,

@@

                yticklabel={%this is a hack to get around the small yrange
                    \pgfmathfloatparse{99.999+\tick/1000}
                    \pgfmathprintnumber{\pgfmathresult}

@@

                %\addplot table[x=NodesFailed,y=VO1]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VO1}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

                %\addplot table[x=NodesFailed,y=VC1]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VC1}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

                %\addplot table[x=NodesFailed,y=VC2]{figures/vm_availability_1000.txt};
                \addplot table[x=NodesFailed,y expr=(\thisrow{VC2}-99.999)*1000]{figures/vm_availability_1000.txt};

@@

        %\caption{1000 machine cluster.}
  \label{fig:vm-availability-1000}
